%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Florian}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Gössele}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Web Frontend Technologies} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Hamburg, DE}\\
	\icon{Phone}{12}{+49 176 7689 5240}\\
	\href{mailto:moin@frot.io}{\icon{Envelope}{12}{moin@frot.io}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\href{https://frot.io}{\icon{Globe}{12}{frot.io}}\\
	\href{https://github.com/frot-io}{\icon{Github}{12}{github.com/frot-io}}\\
	\href{https://twitter.com/@frot\_io}{\icon{Twitter}{12}{@frot\_io}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
  
  Agil, Design Thinking\\
  ``We are what we repeatedly do. Excellence, then, is not an act, but a habit.''
  \href{https://medium.com/the-mission/my-favourite-quote-of-all-time-is-a-misattribution-66356f22843d}{Will Durant}\\
  Web-Technologien begeistern Sie, aber Ihrem Team fehlen die notwendigen Kenntnisse?
 Sie wollen Entwicklungsgeschwindigkeit und Codequalität durch agile Methoden erhöhen?
 Ihr Web-Projekt benötigt Unterstützung eines Experten in der Planung oder Durchführung?
Mit meiner breiten Expertise bin ich in der Lage, Ihr Projekt von der Idee bis zum fertigen Produkt zu
begleiten. Schreiben Sie mir

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{JS}{90}
		\baritem{Angular}{100}
		\baritem{SASS/LESS}{80}
		\baritem{Bootstrap}{90}
		\baritem{Vue}{80}
		\baritem{Typescript}{90}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{5/VS Code, 4/REST, 6/Scrum, 3/TDD, 6/git}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{12/2018 -- present\\\footnotesize{part time}}
		{Full stack developer}
		{\href{https://www.ramstein-kampagne.eu/}{Stopp Air Base Ramstein Campaign}}
    {
      Designing and implementing a \textbf{Progressive Web App} for mobile-first use. The app allows a user to build his/her own calendar from
      the list of all events by marking events as favorite. \textbf{Push-Notifications} will be sent when a change occurs, e.g. when the event is
      rescheduled. The project is non-profit and the code open-source on \underline{\href{https://github.com/frot-io/ramstein-conference-app}{Github}}.
      A live demo is available on \underline{\href{https://ramstein-conference-app.herokuapp.com/}{Heroku}}\\
      \texttt{Angular 7}\slashsep\texttt{Material Design}\slashsep\texttt{NodeJS}\slashsep\texttt{MongoDB}\slashsep\texttt{Heroku}
    }
  \entry
		{4/2018 -- 3/2019}
		{Frontend developer}
		{Deutsche Telekom AG}
    {
      Developing a web-application to enter and modify complex language models. As part of the team \textbf{Machine Learning} in the project
      \underline{\href{https://www.telekom.de/zuhause/geraete-und-zubehoer/smart-speaker}{Smart Speaker}} we provided an interface for a team
      of Linguists and Editors with which they could train the model to better understand the consumer.\\
      \texttt{Angular 5-7}\slashsep\texttt{ngrx}\slashsep\texttt{Bootstrap}\slashsep\texttt{Scrum}\slashsep\texttt{Vue.js}
    }
	\entry
		{3/2018 -- 5/2018\\\footnotesize{part time}}
		{Frontend developer}
		{Pflege zu Hause Küffel GmbH}
		{
      Support in developing a \textbf{Redux}-based web-application for distributing nursing staff to elderly people in need of care\\
      \texttt{React.js}\slashsep\texttt{Bootstrap}\slashsep\texttt{jQuery Widgets}
    }
  \entry
		{08/2016 -- 3/2018\\\footnotesize{part time}}
		{Trainer}
		{Opitz Consulting}
		{
      Trainer for modern web-technologies. I gave introductions in web-development to beginners (e.g. how \textbf{SPA}s work) as well as
      coaching for highly skilled programmers in special use-cases (e.g. introduction to \textbf{Reactive Programming}).\\
      \texttt{Angular 2-5}\slashsep\texttt{Git}\slashsep\texttt{HTML5}\slashsep\texttt{CSS3}
    }
  \entry
		{10/2017 -- 3/2018}
		{Project lead}
		{Eurogate GmbH \& Co. KGaA, KG (via Opitz Consulting)}
		{
      Designing and implementing a system for data-handling in complex container-logistics. I introduced \textbf{agile development} and designed
      the workflow for the deployment in a limited amount of time. In a team of two, we created View-Components in \textbf{npm-Packages} for
      cross-project use.\\ 
      \texttt{Angular 5}\slashsep\texttt{npm}\slashsep\texttt{Living Styleguide}\slashsep\texttt{Scrum}
    }
  \entry
		{10/2017}
		{Frontend architect}
		{YOMA Solutions GmbH (via Opitz Consulting)}
		{
      Creating a \textbf{Proof of Concept} Application in the Cloud as a \textbf{microservice} TODO: for what?
      \texttt{Angular 4}\slashsep\texttt{AWS}\slashsep\texttt{Scrum}\slashsep\texttt{Bootstrap}
    }
  \entry
		{9/2016 -- 9/2017}
		{Frontend developer}
		{Comdirect Bank AG (via Opitz Consulting)}
		{
      TODO\\
      \texttt{JS}\slashsep\texttt{jQuery}\slashsep\texttt{JSP}\slashsep\texttt{Atomic Design}
    }
  \entry
		{7/2016 -- 8/2017}
		{Project lead}
		{Comdirect Bank AG (via Opitz Consulting)}
		{
      TODO\\
      \texttt{Angular 2}\slashsep\texttt{Bootstrap}\slashsep\texttt{D3.js}\slashsep\texttt{Stylus}
    }
  \entry
		{2/2016 -- 7/2016}
		{Developer}
		{Libri GmbH (via Opitz Consulting)}
		{
      TODO\\
      \texttt{Java}\slashsep\texttt{XSLT}\slashsep\texttt{Apache}
    }
  \entry
		{9/2015 -- 12/2015\\\footnotesize{part time}}
		{Teamlead Frontend}
		{yunity.org}
		{
      TODO\\
      \texttt{Angular.js}\slashsep\texttt{Scrum}\slashsep\texttt{Apache}
    }
  \entry
		{7/2015 -- 8/2015\\\footnotesize{part time}}
		{Trainer}
		{Goethe Gymnasium Hamburg}
		{
      TODO\\
      \texttt{Wordpress}
    }
  \entry
		{9/2014 -- 6/2015}
		{Developer}
		{AppVantage GmbH \& Co. KG}
		{
      TODO\\
      \texttt{Ruby on Rails}\slashsep\texttt{C\#}\slashsep\texttt{ORM}\slashsep\texttt{iOS}
    }
  \entry
		{11/2013 -- 8/2014}
		{Developer}
		{e.solutions GmbH}
		{
      TODO\\
      \texttt{Java}\slashsep\texttt{Android}\slashsep\texttt{Scrum}
    }
  \entry
		{11/2012 -- 10/2013}
		{Developer}
		{Fraunhofer Institute for Integrated Circuits}
		{
      TODO\\
      \texttt{C++}\slashsep\texttt{MIPS-32}\slashsep\texttt{Kanban}
    }
  \entry
		{2/2012 -- 10/2012}
		{Trainee}
		{Siemens AG, Sector Energy}
		{
      TODO\\
      \texttt{MS Office}\slashsep\texttt{Windows 7}
    }
  \entry
		{2/2012 -- 10/2012}
		{Tutor}
		{Friedrich–Alexander University Erlangen–Nuremberg}
		{
      TODO\\
      \texttt{Java}\slashsep\texttt{Graphic Algorithms}
    }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2012 -- 2014}
		{Information and Communication Technology}
		{Friedrich–Alexander University Erlangen–Nuremberg}
		{
      Graduation: Bachelor's Degree\\
      Thesis topic: \textit{Design and implementation of a recording system for the bit eXpress broadcast data stream}
      }
	\entry
		{2009 -- 2012}
		{Computational Engineering}
		{Friedrich–Alexander University Erlangen–Nuremberg}
		{Participation in student representative body}
	\entry
		{2008 -- 2009}
		{Mechanical Engineering}
		{Friedrich–Alexander University Erlangen–Nuremberg}
		{Including first mandatory internship}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{German} - native\\
	\textbf{English} - proficient\\
	\textbf{Spanish} - basic\\
	\textbf{French} - basic\\
	\textbf{Swedish} - basic
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	I love Snowboarding and cycling, also on occassion volleyball. I love cooking and to try out new things TODO
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
	
	I help with Foodsharing, HOPAD and am climate aware. I want to make the world a better place TODO
\end{minipage}

%----------------------------------------------------------------------------------------
%	FOOTNOTE
%----------------------------------------------------------------------------------------

\blfootnote{Made with \LaTeX}

%----------------------------------------------------------------------------------------

\end{document}
